%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%
%%%	MSEE THESIS MASTER DOCUMENT
%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% PREAMBLE

\documentclass[12pt,letterpaper]{report}
\usepackage{indentfirst}
\usepackage{sectsty,titlesec}
\usepackage[titles]{tocloft}
\usepackage{MEJ_MSEE}
\usepackage{setspace}
\usepackage{psfrag,graphicx,epsfig,array}
\usepackage{amsmath,amsfonts,amssymb,amsthm,amsxtra}
\usepackage{bm}
\usepackage{multirow,booktabs}
\usepackage{caption}
\usepackage{checkend}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{rotating}
\usepackage{float}
% \usepackage{layout}

\usepackage{lmodern}
\usepackage[T1]{fontenc}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% FUNCTIONS

\newcommand{\CTDSM}		{Continuous-Time $\Delta\Sigma$ Modulator }
\newcommand{\DTDSM}		{Discrete-Time $\Delta\Sigma$ Modulator }
\newcommand{\CTDSMs}	{Continuous-Time $\Delta\Sigma$ Modulators }
\newcommand{\DTDSMs}	{Discrete-Time $\Delta\Sigma$ Modulators }
\newcommand{\DSM}		{$\Delta\Sigma$ Modulator }
\newcommand{\DSMs}		{$\Delta\Sigma$ Modulators }
\newcommand{\DSm}		{$\Delta\Sigma$ modulator }
\newcommand{\DSms}		{$\Delta\Sigma$ modulators }
\newcommand{\DS}		{$\Delta\Sigma$\space}
\newcommand{\CT}		{Continuous-Time }
\newcommand{\DT}		{Discrete-Time }
\newcommand{\ct}		{continuous-time }
\newcommand{\dt}		{discrete-time }
\newcommand{\ntf}		{noise transfer function }
\newcommand{\stf}		{signal transfer function }
\newcommand{\wrt}		{with respect to }
\newcommand{\nth}		{$n$th}
\newcommand{\ith}		{$i$th}
\newcommand{\mc}[3]		{\multicolumn{#1}{#2}{#3}}
\newcommand{\mr}[2]		{\multirow{#1}*{#2}}
\newcommand{\norm}[1]	{\lVert#1\rVert}
\newcommand{\abs}[1]	{\lvert#1\rvert}
\newcommand{\fix}[1] 	{\texorpdfstring{#1}}
\newcommand{\NTF}		{\mathop\text{NTF}}
\newcommand{\STF}		{\mathop\text{STF}}

\makeatletter
\newcommand*\dashline{\rotatebox[origin=c]{90}{$\dabar@\dabar@\dabar@$}}
\makeatother

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% DOCUMENT BODY
\begin{document}

\mastersthesis
\renewcommand{\thesisauthor}		{Matthew Edward Jackson}
\renewcommand{\thesismonth}			{August}
\renewcommand{\thesisdefensemonth}	{June}
\renewcommand{\thesisyear}			{2009}
\renewcommand{\thesistitle}
{Optimal Design of Discrete-Time \\ Delta Sigma Modulators}
\renewcommand{\thesissupervisor}	{Peter Allen Stubberud}
\renewcommand{\thesistype}			{thesis}
\renewcommand{\thesisdegree}		{Master of Science}
\renewcommand{\thesisdedication}	{To my dog.}
\renewcommand{\thesisfrontheadsize}	{\normalsize}

% FRONT MATTER
\thesistitlepage
\thesiscopyrightpage
% \thesissignaturepage

% ABSTRACT
\newpage
\phantomsection
\addcontentsline{toc}{chapter}{ABSTRACT}
\begin{thesisabstract}
\pagenumbering{roman}
\setcounter{page}{3}
\par
In this thesis, optimal signal transfer functions (STFs) and noise transfer functions
(NTFs) for discrete time delta sigma ($\Delta\Sigma$) modulators are determined.  For a
given oversampling rate (OSR), these STFs and NTFs are optimized with respect to a
weighted
combination of the \DS modulator's signal-to-noise ratio (SNR) and dynamic range (DR).
This optimization problem is solved using a novel hybrid orthogonal genetic (HOG)
algorithm that uses customized genetic operators to improve algorithm performance and
accuracy when applied to multimodal, non-differentiable performance surfaces. To
generate optimal system functions, the HOG algorithm is implemented as a constrained
global optimizer to minimize cost functions which represent approximations of the system
functions.
\end{thesisabstract}

\tableofcontents
\listoffigures
\listoftables

% ACKNOWLEDGMENTS
\newpage
\phantomsection
\addcontentsline{toc}{chapter}{ACKNOWLEDGMENTS}
\begin{thesisacknowledgements}
 \par
I would like to thank my advisor, Dr. Peter Stubberud, for the countless hours he invested
in this work. Moreover, I would like to thank his wife, Laura, for her patience and wisdom
which always prevailed when cooler heads did not. Without her compassion this effort would
have fallen well short of its mark. Secondly, I would like to thank my wife, Alicia, and
all of my wonderful daughters for being supportive and understanding despite all the long
weekends, late nights, and missed soccer games.

From a young age my family instilled in me a deep value for education built upon
respect for the educated and an appreciation for the hard work and perseverance
required to attain it. Thus, this work is dedicated to the educated men who inspired me:
 my grandfathers, Dr. Clyde T. Stoner and Dr. Raymond Van Pelt, and my father, Dr.
Fredrick L. Jackson.
\end{thesisacknowledgements}

\doublespacing

% CHAPTER 1: INTRODUCTION
\chapter{INTRODUCTION}
\label{ch:Introduction}
\pagenumbering{arabic}
\input{Introduction}

% CHAPTER 2: BACKGROUND
\chapter{ANALOG-TO-DIGITAL CONVERTERS}
\label{ch:ADCs and DSMs}
\input{ADCs_DSMs}

% CHAPTER 3: HOG ALGORITHM
\chapter{OPTIMIZATION AND GENETIC ALGORITHMS}
\label{ch:Optimization and Genetic Algorithms}
\input{optimization_hoga}

% CHAPTER 4: DSM DESIGN IMPLEMENTAION AND RESULTS
\chapter{IMPLEMENTATION AND RESULTS}
\label{ch:Implementation and Results}
\input{implementation_results}

% CHAPTER 5: CONCLUSION
\chapter{CONCLUSION}
\label{ch:Conclusion}
\input{conclusion}

% BIBLIOGRAPHY
\titlespacing*{\chapter}{0pt}{50pt}{\baselineskip}
\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{REFERENCES}
\begin{spacing}{1}
	\bibliography{new_bib}
	\bibliographystyle{plain}
\end{spacing}

% VITA
\newpage
\phantomsection
\addcontentsline{toc}{chapter}{VITA} 
\thesisauthorvita

\end{document}